Manuscript progress report

### 2023-12-05 Docs/manuscript.Rmd
small scale simulation 100 iterations

# Small-scale simulation: one iteration

@@

$$g(E(Y_i(t))) = \sum_{k=1}^5\zeta_{k}B_k(t)+\sum_{l=1}^5\xi_{il}\phi_l(t)$$

I did the following things for data-reduction

- Reduce sample size to 10 (for both training and testing)
- Reduce measurement track by half (0.25-0.75)
- Another way is the simple reduce the measurement density. For example, instead of every minute, we can use every 10 minutes. In this case, the binning step in fGFPCA would bin every 100 minutes in to one bin. 
- - When we have smaller density of measurement grid, both methods could run into numeric issues in both methods. For example, singularity happened the the local GLMM step of fGFPCA procedure. This might be able to get resoved by changing the optimizer (e.g. Nealder_Mead). Do we want to do that? Or perhaps we simply want to use the full track?

- We may also need to reduce number of simulations (GLMMadaptive took 20-ish minutes for one simulaiton).

Below are some of the outcomes:

@@

```{r fig_pred_subset}
fig_fgfpca_subset <- df_pred_m_fGFPCA %>% filter(id %in% 501:504) %>%
  mutate_at(vars(eta_i, pred0.35, pred0.45, pred0.55, pred0.65), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.35, col = "0.35"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.45, col = "0.45"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.55, col = "0.55"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.65, col = "0.65"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "fGFPCA", col = "Maximum observation time")

fig_adglmm_subset <- df_pred_m_adglmm %>% filter(id %in% 501:504) %>%
  mutate_at(vars(eta_i, pred0.35, pred0.45, pred0.55, pred0.65), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.35, col = "0.35"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.45, col = "0.45"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.55, col = "0.55"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.65, col = "0.65"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "GLMMadaptive", col = "Maximum observation time")

@@

```{r ise_fGFPCA_subset}
window2 <- seq(0.25, 0.75, by = 0.1)
ise_mat_subset <- df_pred_m_fGFPCA %>%
    mutate(err1 = (pred0.35-eta_i)^2,
           err2 = (pred0.45-eta_i)^2,
           err3 = (pred0.55-eta_i)^2,
           err4 = (pred0.65-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window2, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0.25,0.35]") %>% 
    select(starts_with("err"))
colnames(ise_mat_subset) <- c("(0.25,0.35]", "(0.25,0.45]", "(0.25,0.55]", "(0.25,0.65]")
```

```{r ise_GLMMadaptive_subset}
ise_mat_subset2 <- df_pred_m_adglmm %>%
    mutate(err1 = (pred0.35-eta_i)^2,
           err2 = (pred0.45-eta_i)^2,
           err3 = (pred0.55-eta_i)^2,
           err4 = (pred0.65-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window2, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0.25,0.35]") %>% 
    select(starts_with("err"))
colnames(ise_mat_subset2) <- c("(0.25,0.35]", "(0.25,0.45]", "(0.25,0.55]", "(0.25,0.65]")
```

```{r}
data.frame(Window = c("(0.35,0.45]", "(0.45,0.55]", "(0.55,0.65]", "(0.65, 0.75]"),
           ise_mat_subset, ise_mat_subset2, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

@@

```{r auc_fGFPCA_subset}
auc_mat_subset <- df_pred_m_fGFPCA %>%
  mutate(window = cut(t, breaks = window2, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred0.35),
            auc2 = get_auc(Y, pred0.45),
            auc3 = get_auc(Y, pred0.55),
            auc4 = get_auc(Y, pred0.65)) %>%
  filter(window != "[0.25,0.35]") %>% 
  select(starts_with("auc"))

colnames(auc_mat_subset) <- c("(0.25,0.35]", "(0.25,0.45]", "(0.25,0.55]", "(0.25,0.65]")
```

```{r auc_GLMMadaptive_subset}
auc_mat_subset2 <- df_pred_m_adglmm %>%
  mutate(window = cut(t, breaks = window2, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred0.35),
            auc2 = get_auc(Y, pred0.45),
            auc3 = get_auc(Y, pred0.55),
            auc4 = get_auc(Y, pred0.65)) %>%
  filter(window != "[0.25,0.35]") %>% 
  select(starts_with("auc"))

colnames(auc_mat_subset2) <- c("(0.25,0.35]", "(0.25,0.45]", "(0.25,0.55]", "(0.25,0.65]")
```

```{r}
data.frame(Window = c("(0.35,0.45]", "(0.45,0.55]", "(0.55,0.65]", "(0.65, 0.75]"),
           auc_mat_subset, auc_mat_subset2, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

@@

```{r pred_nhanes, fig.height=4, fig.width=10}
rand_id2 <- sample(unique(nhanes_pred_fgfpca$id), 4)

ggarrange(
  nhanes_pred_fgfpca %>% 
    filter(id %in% rand_id2) %>%
    mutate_at(vars(starts_with("pred")), function(x)exp(x)/(1+exp(x))) %>% 
    ggplot()+
    geom_line(aes(x=t, y = pred480, col = "8am"), linetype = "dashed", na.rm = T)+
    geom_line(aes(x=t, y = pred960, col = "4pm"),linetype = "dashed", na.rm = T)+
    geom_point(aes(x=t, y = Y, col = "Outcome"), size = 0.2)+
    facet_wrap(~id)+
    labs(x = "Time", y = "fGFPCA")+
  scale_x_continuous(breaks = seq(0, 1440, by = 480), 
                     labels = c("Midnight", "8am", "4pm", "Midnight"))+
  theme(axis.text = element_text(size = 5)),

  nhanes_pred_adglmm %>% 
    filter(id %in% rand_id2) %>%
    mutate_at(vars(starts_with("pred")), function(x)exp(x)/(1+exp(x))) %>% 
    ggplot()+
    geom_line(aes(x=t, y = pred480, col = "8am"), linetype = "dashed", na.rm = T)+
    geom_line(aes(x=t, y = pred960, col = "4pm"),linetype = "dashed", na.rm = T)+
    geom_point(aes(x=t, y = Y, col = "Outcome"), size = 0.2)+
    facet_wrap(~id)+
    labs(x = "Time", y = "GLMMadaptive")+
  scale_x_continuous(breaks = seq(0, 1440, by = 480), 
                     labels = c("Midnight", "8am", "4pm", "Midnight"))+
  theme(axis.text = element_text(size = 5)),
  nrow = 1, common.legend = T)
```

```{r small_exp}
# a smaller example of binary functions
df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id2 & Z == 1) %>% 
  mutate(SEQN = as.factor(SEQN)) %>% 
  ggplot()+
  geom_point(aes(x=sind, y = SEQN), size = 0.5)+
  labs(x="Time", y="Subject", title = "NHANES binary activity indicator")
```

@@

```{r binning}
df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id2 & sind >= 650 & sind <= 750) %>% 
  mutate(SEQN = as.factor(SEQN)) %>% 
  ggplot()+
  geom_point(aes(x=sind, y = Z, col = SEQN), size = 0.5)+
  geom_vline(xintercept = seq(650, 750, by = 10), linetype="dashed")+
  scale_y_continuous(breaks = c(0, 1))+
  labs(x="Time", y="", title = "NHANES binary activity indicator")
```

```{r}
df_fig <- df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id2 & sind >= 650 & sind <= 750) %>% 
  mutate(bin = cut(sind, breaks = seq(650, 750, by = 10), 
                   labels = seq(655, 745, by = 10),
                   include.lowest = T)) 
bin_mid <- seq(655, 745, by = 10)

>>>>

# Small-scale simulation

@@

$$g(E(Y_i(t))) = \sum_{k=1}^4\zeta_{k}B_k(t)+\sum_{l=1}^4\xi_{il}\phi_l(t)$$

I have used 100 subjects for training and testing, and repeated 100 times. When fitting GLMMadpative, I reduce the number of measurements to 1/10 by taking one every 10 observations. The prediction is on the original grid.

@@

```{r fig_pred_subset}
rand_id2 <- sample(unique(pred_subset_fGFPCA[[1]]$id), 4)

fig_fgfpca_subset <- pred_subset_fGFPCA[[1]] %>%
  filter(id %in% rand_id2) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "fGFPCA", col = "Maximum observation time")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))

fig_adglmm_subset <- df_subset_adglmm %>% filter(id %in% rand_id2) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "GLMMadaptive", col = "Maximum observation time")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))

@@

```{r}
M2 <- length(pred_subset_fGFPCA)
## ISE container 
ise_mat_subset <- ise_mat_subset_ref <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M2))
```

```{r ise_fGFPCA_subset}
for(m in 1:M2){
  this_df <- pred_subset_fGFPCA[[m]]
  ise_tb_m <- this_df %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err")) %>% as.matrix()
  ise_mat_subset[,,m] <- ise_tb_m
}

ise_mat_subset <- apply(ise_mat_subset, c(1, 2), mean)

colnames(ise_mat_subset) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r ise_GLMMadaptive_subset}
ise_mat_subset2 <- df_subset_adglmm %>%
    mutate(err1 = (pred0.2-eta_i)^2,
           err2 = (pred0.4-eta_i)^2,
           err3 = (pred0.6-eta_i)^2,
           err4 = (pred0.8-eta_i)^2) %>%
    select(id, t, starts_with("err")) %>% 
    mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
    group_by(window, id) %>% 
    summarise_at(vars(err1, err2, err3, err4), sum) %>% 
    group_by(window) %>% 
    summarize_at(vars(err1, err2, err3, err4), mean) %>%
    filter(window != "[0,0.2]") %>% 
    select(starts_with("err"))
colnames(ise_mat_subset2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r}
data.frame(Window = c("(0.2,0.4]", "(0.4,0.6]", "(0.6,0.8]", "(0.8, 1.0]"),
           ise_mat_subset, ise_mat_subset2, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

@@

```{r}
## auc container 
auc_mat_subset <- array(NA, dim = c(length(window)-2, length(window)-2, M2))
auc_mat_subset_ref <- array(NA, dim = c(length(window)-2, length(window)-2, M2))
```

```{r auc_fGFPCA_subset}
for(m in 1:M2){
  this_df <- pred_subset_fGFPCA[[m]]

  auc_tb_m <- this_df %>%
  mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred0.2),
            auc2 = get_auc(Y, pred0.4),
            auc3 = get_auc(Y, pred0.6),
            auc4 = get_auc(Y, pred0.8)) %>%
  filter(window != "[0,0.2]") %>% 
  select(starts_with("auc")) %>% as.matrix()

  auc_mat_subset[, , m] <- auc_tb_m

auc_mat_subset <- apply(auc_mat_subset, c(1,2), mean)
colnames(auc_mat_subset) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r auc_GLMMadaptive_subset}
auc_mat_subset2 <- df_subset_adglmm %>%
  mutate(window = cut(t, breaks = window, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred0.2),
            auc2 = get_auc(Y, pred0.4),
            auc3 = get_auc(Y, pred0.6),
            auc4 = get_auc(Y, pred0.8)) %>%
  filter(window != "[0,0.2]") %>% 
  select(starts_with("auc"))

colnames(auc_mat_subset2) <- c("0.2", "0.4", "0.6", "0.8")
```

```{r}
data.frame(Window = c("(0.2,0.4]", "(0.4,0.6]", "(0.6,0.8]", "(0.8, 1.0]"),
           auc_mat_subset, auc_mat_subset2, check.names = F) %>%
  kable(digits = 3, caption = "Integrated squared error") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" "= 1, "Observation track" = 8))
```

@@

```{r pred_nhanes, fig.height=4, fig.width=10}
rand_id3 <- sample(unique(nhanes_pred_fgfpca$id), 4)

ggarrange(
  nhanes_pred_fgfpca %>% 
    filter(id %in% rand_id3) %>%
    mutate_at(vars(starts_with("pred")), function(x)exp(x)/(1+exp(x))) %>% 
    ggplot()+
    geom_line(aes(x=t, y = pred480, col = "8am"), linetype = "dashed", na.rm = T)+
    geom_line(aes(x=t, y = pred960, col = "4pm"),linetype = "dashed", na.rm = T)+
    geom_point(aes(x=t, y = Y, col = "Outcome"), size = 0.2)+
    facet_wrap(~id)+
    labs(x = "Time", y = "fGFPCA")+
  scale_x_continuous(breaks = seq(0, 1440, by = 480), 
                     labels = c("Midnight", "8am", "4pm", "Midnight"))+
  theme(axis.text = element_text(size = 5)),

  nhanes_pred_adglmm %>% 
    filter(id %in% rand_id3) %>%
    mutate_at(vars(starts_with("pred")), function(x)exp(x)/(1+exp(x))) %>% 
    ggplot()+
    geom_line(aes(x=t, y = pred480, col = "8am"), linetype = "dashed", na.rm = T)+
    geom_line(aes(x=t, y = pred960, col = "4pm"),linetype = "dashed", na.rm = T)+
    geom_point(aes(x=t, y = Y, col = "Outcome"), size = 0.2)+
    facet_wrap(~id)+
    labs(x = "Time", y = "GLMMadaptive")+
  scale_x_continuous(breaks = seq(0, 1440, by = 480), 
                     labels = c("Midnight", "8am", "4pm", "Midnight"))+
  theme(axis.text = element_text(size = 5)),
  nrow = 1, common.legend = T)
```

```{r small_exp}
# a smaller example of binary functions
df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & Z == 1) %>% 
  mutate(SEQN = as.factor(SEQN)) %>% 
  ggplot()+
  geom_point(aes(x=sind, y = SEQN), size = 0.5)+
  labs(x="Time", y="Subject", title = "NHANES binary activity indicator")
```

@@

```{r binning}
df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & sind >= 650 & sind <= 750) %>% 
  mutate(SEQN = as.factor(SEQN)) %>% 
  ggplot()+
  geom_point(aes(x=sind, y = Z, col = SEQN), size = 0.5)+
  geom_vline(xintercept = seq(650, 750, by = 10), linetype="dashed")+
  scale_y_continuous(breaks = c(0, 1))+
  labs(x="Time", y="", title = "NHANES binary activity indicator")
```

```{r}
df_fig <- df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & sind >= 650 & sind <= 750) %>% 
  mutate(bin = cut(sind, breaks = seq(650, 750, by = 10), 
                   labels = seq(655, 745, by = 10),
                   include.lowest = T)) 
bin_mid <- seq(655, 745, by = 10)

### 2023-12-05 Docs/manuscript.tex
small scale simulation 100 iterations

\title{Manuscript progress report}
\author{Ying Jin}
\date{2023-12-04}

@@

\[g(E(Y_i(t))) = \sum_{k=1}^5\zeta_{k}B_k(t)+\sum_{l=1}^5\xi_{il}\phi_l(t)\]

I did the following things for data-reduction

\begin{itemize}
\item
  Reduce sample size to 10 (for both training and testing)
\item
  Reduce measurement track by half (0.25-0.75)
\item
  Another way is the simple reduce the measurement density. For example,
  instead of every minute, we can use every 10 minutes. In this case,
  the binning step in fGFPCA would bin every 100 minutes in to one bin.
\item
  \begin{itemize}
  \tightlist
  \item
    When we have smaller density of measurement grid, both methods could
    run into numeric issues in both methods. For example, singularity
    happened the the local GLMM step of fGFPCA procedure. This might be
    able to get resoved by changing the optimizer (e.g.~Nealder\_Mead).
    Do we want to do that? Or perhaps we simply want to use the full
    track?
  \end{itemize}
\item
  We may also need to reduce number of simulations (GLMMadaptive took
  20-ish minutes for one simulaiton).
\end{itemize}

Below are some of the outcomes:

@@

\caption{\label{tab:unnamed-chunk-8}Integrated squared error}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{8}{c}{Observation track} \\
\cline{2-9}
\multicolumn{1}{c|}{ } & \multicolumn{4}{c|}{fGFPCA} & \multicolumn{4}{c}{GLMMadaptive} \\
\cline{2-5} \cline{6-9}
Window & (0.25,0.35] & (0.25,0.45] & (0.25,0.55] & (0.25,0.65] & (0.25,0.35] & (0.25,0.45] & (0.25,0.55] & (0.25,0.65]\\
\hline
(0.35,0.45] & 35.724 &  &  &  & 48.779 &  &  & \\
\hline
(0.45,0.55] & 77.379 & 22.690 &  &  & 74.537 & 34.232 &  & \\
\hline
(0.55,0.65] & 32.581 & 20.370 & 20.043 &  & 48.683 & 35.666 & 18.303 & \\
\hline
(0.65, 0.75] & 158.191 & 135.968 & 130.360 & 66.648 & 174.158 & 141.285 & 143.370 & 103.92\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-9}Integrated squared error}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{8}{c}{Observation track} \\
\cline{2-9}
\multicolumn{1}{c|}{ } & \multicolumn{4}{c|}{fGFPCA} & \multicolumn{4}{c}{GLMMadaptive} \\
\cline{2-5} \cline{6-9}
Window & (0.25,0.35] & (0.25,0.45] & (0.25,0.55] & (0.25,0.65] & (0.25,0.35] & (0.25,0.45] & (0.25,0.55] & (0.25,0.65]\\
\hline
(0.35,0.45] & 0.657 &  &  &  & 0.643 &  &  & \\
\hline
(0.45,0.55] & 0.611 & 0.690 &  &  & 0.624 & 0.702 &  & \\
\hline
(0.55,0.65] & 0.687 & 0.710 & 0.714 &  & 0.666 & 0.686 & 0.702 & \\
\hline
(0.65, 0.75] & 0.604 & 0.639 & 0.636 & 0.653 & 0.598 & 0.593 & 0.587 & 0.62\\
\hline
\end{tabular}
\end{table}

>>>>

\title{Manuscript progress report}
\author{Ying Jin}
\date{2023-12-05}

@@

\[g(E(Y_i(t))) = \sum_{k=1}^4\zeta_{k}B_k(t)+\sum_{l=1}^4\xi_{il}\phi_l(t)\]

I have used 100 subjects for training and testing. When fitting
GLMMadpative, I reduce the number of measurements to 1/10 by taking one
every 10 observations. The prediction is on the original grid.

@@

\caption{\label{tab:unnamed-chunk-8}Integrated squared error}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{8}{c}{Observation track} \\
\cline{2-9}
\multicolumn{1}{c|}{ } & \multicolumn{4}{c|}{fGFPCA} & \multicolumn{4}{c}{GLMMadaptive} \\
\cline{2-5} \cline{6-9}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\hline
(0.2,0.4] & 154.178 &  &  &  & 387.140 &  &  & \\
\hline
(0.4,0.6] & 168.881 & 70.248 &  &  & 248.395 & 415.355 &  & \\
\hline
(0.6,0.8] & 235.562 & 47.770 & 16.813 &  & 330.585 & 321.804 & 265.975 & \\
\hline
(0.8, 1.0] & 97.413 & 77.682 & 19.947 & 12.015 & 186.022 & 525.561 & 349.314 & 116.319\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-9}Integrated squared error}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{8}{c}{Observation track} \\
\cline{2-9}
\multicolumn{1}{c|}{ } & \multicolumn{4}{c|}{fGFPCA} & \multicolumn{4}{c}{GLMMadaptive} \\
\cline{2-5} \cline{6-9}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\hline
(0.2,0.4] & 0.721 &  &  &  & 0.646 &  &  & \\
\hline
(0.4,0.6] & 0.658 & 0.725 &  &  & 0.620 & 0.665 &  & \\
\hline
(0.6,0.8] & 0.710 & 0.793 & 0.805 &  & 0.682 & 0.700 & 0.733 & \\
\hline
(0.8, 1.0] & 0.712 & 0.725 & 0.761 & 0.764 & 0.647 & 0.582 & 0.657 & 0.725\\
\hline
\end{tabular}
\end{table}
